%-------------------------
% Resume in Latex
% Author : based on Jake Gutierrez Jake's Resume (Anonymous)
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

% \documentclass[letterpaper,11pt]{article}
\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}



\usepackage{enumitem} % For more control over lists
\usepackage{textcomp}
\usepackage{amsmath}
\usepackage{bm}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
\usepackage{charter}



% In your preamble, define a grey color
\usepackage{xcolor}
\definecolor{grey}{rgb}{0.5, 0.5, 0.5}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}



% --- FINAL, CORRECTED CUSTOM COMMAND ---
\newcommand{\resumeSubheadingSingleLine}[4]{
  \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{#2} \\
      \if\relax\detokenize{#3}\relax\else
        \textit{\small#3} & \textit{\small #4} \\
      \fi
    \end{tabular*}
    \vspace{-2pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
        \large{#1} & \textit{#2} \\
    \end{tabular*}
}


%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\noindent\textcolor{grey}{\small\hfill Last Updated: \today}
\vspace{-1em} % Negative space to pull the next section up a bit

\begin{center}
    {\Huge \scshape Isaac Bernat} \\ \vspace{1pt}
    \small 
    \href{https://www.isaacbernat.com/cv}{Portfolio: isaacbernat.com/cv} ~ \textbullet ~
    \href{mailto:cv@isaacbernat.com}{ 
    % \textbf{Email:}
    % \underline{cv@isaacbernat.com}} ~ \textbullet ~
    cv@isaacbernat.com} ~ \textbullet ~
    \href{https://linkedin.com/in/isaacbernat}{linkedin.com/in/isaacbernat} ~ \textbullet ~
    \href{https://github.com/isaacbernat}{github.com/isaacbernat}
    \vspace{-8pt}
\end{center}


%----------------------------------------------------------------------------------------
%   PROFESSIONAL SUMMARY
% %----------------------------------------------------------------------------------------

\vspace{0.2em} % Slightly reduced top margin
\begin{center}
    \begin{minipage}{0.85\textwidth} % Slightly wider container
        \small \textit{Staff Software Engineer with 12+ years of experience in backend systems and product strategy. A proven leader of high-impact initiatives, including architecting a core subscription platform instrumental in a \textbf{Series C funding round}, and delivering a \textbf{+3\% global Gross Margin lift} on a separate monetization project.}
    \end{minipage}
\end{center}
\vspace{-0.7em} % Slightly more negative bottom margin


%-----------EXPERIENCE-----------
\section{Professional Experience}
\begin{itemize}[leftmargin=*, topsep=0pt, partopsep=0pt, itemsep=1em, parsep=0pt] % Main experience list

\item % Independent Sabbatical
    \textbf{Independent Professional Development} \hfill \textit{Aug 2024 – Present} \\
    \begin{itemize}[leftmargin=1.5em, topsep=2pt, itemsep=2pt]
        \item Authored a production-level system design for a heuristic-based Spam Classification Engine.
        \item Developed open-source tools, including 
        \href{https://github.com/isaacbernat/basepaint-media/}{ a Python/LLM data pipeline } and \href{https://github.com/isaacbernat/netflix-to-srt/}{ `netflix-to-srt` (800+ GH stars)}.
    \end{itemize}
\end{itemize}

\vspace{0.5em} % Add a bit of space between job entries
\noindent % Prevents any weird indentation
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}c@{\extracolsep{\fill}}r}
    \textbf{\Large Preply} & \textit{Mar 2020 – Jul 2024} & \textbf{Barcelona, Spain (Remote)} \\
\end{tabular*}

\begin{itemize}[leftmargin=*, topsep=4pt, partopsep=0pt, itemsep=8pt, parsep=0pt] % Roles within Preply
    \item \textbf{Staff Backend Engineer} \hfill \textit{Jun 2022 – Jul 2024}
        \begin{itemize}[leftmargin=1.5em, topsep=2pt, itemsep=4pt]
                \item Drove the company's \#1 most impactful initiative of 2023 (out of 215 A/B tests), delivering a \textbf{+3\% global Gross Margin lift} by overhauling subscription cancellation and pause policies. \href{https://www.isaacbernat.com/cv#casestudy-postpone-billing}{\underline{Case study available online}}
                \item Acted as a strategic technical advisor, identifying critical risks in a major initiative and advocating for a phased approach that mitigated over \textbf{10,000 hours} in potential wasted development.
                \item Proactively identified and mitigated a critical financial exploit by designing and implementing a rate-limiting solution that preserved legitimate user functionality.
                \item Exhibited cross-domain ownership by resolving critical bugs outside my team's direct responsibility, including a promotions flaw costing \textbf{\$21,000/week} and a runaway task executing over \textbf{1M times/hour}.
                \item Championed and improved engineering best practices, including advocating for enhanced observability and establishing a new, mandatory pre-launch monitoring policy that was adopted company-wide.

                % RESUME ITEM HAS SMALLER FONT!!
                % \resumeItem{Exhibited cross-domain ownership by proactively identifying and leading the mitigation of critical production bugs, including a promotions flaw costing \textbf{\$21,000/week} and a runaway Celery task executing over \textbf{1M times/hour}.}
            \end{itemize}
        
        \item \textbf{Senior Backend Engineer} \hfill \textit{Mar 2020 – Jun 2022}
            \begin{itemize}[leftmargin=1.5em, topsep=2pt, itemsep=4pt]
                \item Served as the founding backend architect for the Subscription MVP, designed the core services and orchestrated the cross-team integrations (Payments, CRM, Data, Customer Success) required for a new recurring revenue system. This foundational work delivered a \textbf{+41\% YoY increase in LTV}, improved the \textbf{LTV-to-CAC ratio from 1.4x to 3.0x} and was instrumental in securing a \textbf{Series C funding round}. \href{https://www.isaacbernat.com/cv#casestudy-subscription-model}{\underline{Case study available online}}
                \item Commanded 15+ production incidents and used the post-mortem from a critical SEV-2 to establish a mandatory, company-wide policy on pre-launch monitoring and observability.
                \href{https://www.isaacbernat.com/cv#casestudy-incident-74}{\underline{Case study available online}}
                \item Led the backend migration of a high-traffic (1M+ MAU) application to a GraphQL API, improving page load times by \textbf{\textgreater85\%} and unblocking A/B tests that resulted in an \textbf{+800\% CVR increase}.
                \item Played a key role in scaling the dedicated Subscriptions team by interviewing 13 candidates and hiring 2 of its foundational engineers. Improved team agility by redesigning our sprint retrospective process, increasing actionable outcomes.
            \end{itemize}
    \end{itemize}


% --- Ivbar Institute ---
\vspace{0.5em}
\noindent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{\Large Ivbar Institute} & \textbf{Stockholm, Sweden} \\
\end{tabular*}
\begin{itemize}[leftmargin=*, topsep=4pt, partopsep=0pt, itemsep=2pt, parsep=0pt]
    \item \textbf{Fullstack Engineer} \hfill \textit{Mar 2018 – Mar 2020}
        \begin{itemize}[leftmargin=1.5em, topsep=2pt, itemsep=4pt]
            \item Architected the core data processing engine for the Swedish National Quality Registry for Breast Cancer (NKBC), enabling nationwide analysis of treatment outcomes.
            \item Implemented MECE-compliant privacy filters to ensure patient k-anonymity in highly sensitive medical datasets, a critical requirement for ethical handling of PII.
            \item Engineered a React-based UI for complex medical case-mix decision trees, empowering healthcare professionals to better analyze treatment pathways.
        \end{itemize}
\end{itemize}


% --- Productos Aditivos ---
\vspace{0.5em}
\noindent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{\Large Productos Aditivos} & \textbf{Montcada, Spain} \\
\end{tabular*}
\begin{itemize}[leftmargin=*, topsep=4pt, partopsep=0pt, itemsep=2pt, parsep=0pt]
    \item \textbf{CTO \& CFO} \hfill \textit{Jun 2016 – Jan 2018}
        \begin{itemize}[leftmargin=1.5em, topsep=2pt, itemsep=4pt]
            \item Drove technology modernization and financial optimization, securing over \textbf{€64,000 in savings} by renegotiating commercial loans and rectifying payroll errors.
            \item Oversaw a critical ERP migration and the company-wide transition to the Spanish SII tax reporting system.
        \end{itemize}
\end{itemize}


% --- Wrapp ---
\vspace{0.5em}
\noindent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}c@{\extracolsep{\fill}}r}
    \textbf{\Large Wrapp} & \textit{Oct 2012 – Jun 2016} & \textbf{Stockholm, Sweden} \\
\end{tabular*}
\begin{itemize}[leftmargin=*, topsep=4pt, partopsep=0pt, itemsep=8pt, parsep=0pt]
    \item \textbf{Tech Lead} \hfill \textit{Sep 2014 – Jun 2016}

    \begin{itemize}[leftmargin=1.5em, topsep=2pt, itemsep=4pt]
        \item Guided the architectural transition from a monolith to a distributed system of \textbf{50+ microservices}.
        \item Owned and maintained critical backend services like `users` (Python). As maintainer of the `offers` (Go), I was responsible for code quality and consistency across \textbf{1,200+ commits} and 12 contributors.
        \item Architected the core backend APIs for mapping credit card transactions to merchant offers.
        \item Designed and built "Opsweb," a mission-critical CI/CD platform for managing canary releases, cluster health monitoring and automated rollbacks, which directly improved developer velocity and site reliability.
    \end{itemize}
    \item \textbf{Early Engineer (Backend, Data, Frontend)} \hfill \textit{Oct 2012 – Sep 2014}
    \begin{itemize}
        \item Developed and maintained a heuristic-based fraud prevention system to detect and block abuse of the platform’s gift card and coupon features, protecting against financial loss from fake user profiles.
        \item Engineered foundational data systems, including the company's first content recommendation engine and a high-volume ETL pipeline for our Redshift data warehouse.
        \item Collaborated effectively in an asynchronous environments with teams in Stockholm and San Francisco.
    \end{itemize}
\end{itemize}

% --- FXstreet.com ---
\vspace{0.5em}
\noindent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{\Large FXstreet.com} & \textbf{Barcelona, Spain} \\
\end{tabular*}
\begin{itemize}[leftmargin=*, topsep=4pt, partopsep=0pt, itemsep=2pt, parsep=0pt]
    \item \textbf{Software Developer} \hfill \textit{Feb 2012 – Jul 2012}
        \begin{itemize}[leftmargin=1.5em, topsep=2pt, itemsep=4pt]
            \item Contributed to a high-traffic C\#/.NET financial news portal, handling complex internationalization (i18n) challenges across \textbf{17 languages}.
        \end{itemize}
\end{itemize}


%----------------------------------------------------------------------------------------
%   KEY PROJECTS & PRESENTATIONS
%----------------------------------------------------------------------------------------
% \vspace{0.5em plus 0.3em minus 0.2em}


\section{Key Projects \& Presentations}
\resumeSubHeadingListStart
    \resumeProjectHeading
        {\textbf{System Design: Heuristic-based Spam Classifier}}{}
        \resumeItemListStart
            \resumeItem{Authored a production-level technical design for a proof-of-concept spam classifier, demonstrating a pragmatic approach to building new features within legacy ecosystems. 
            \href{https://www.isaacbernat.com/cv#system-design}{\underline{Document available online}}}
        \resumeItemListEnd
\vspace{-1.0em}


\resumeProjectHeading
    {\textbf{PyCon Sweden 2019: Deep Dive on Python Performance}}{}
    \resumeItemListStart
        \resumeItem{Presented iterative code optimizations. Demonstrated how to diagnose, analyze and solve bottlenecks with CPython bytecode, profilers and low-level system tooling. Showcased speedup techniques achieve {\boldmath\textbf{$>10^{18}$x improvements}}.
            \href{https://youtu.be/asZ0SDTKqvM}{\underline{Talk available on YouTube}}
        }
    \resumeItemListEnd
\vspace{-1.0em}


\resumeProjectHeading
    {\textbf{PyCon Sweden 2014: Building Developer Tooling}}{}
    \resumeItemListStart
        \resumeItem{Selected to speak at the inaugural PyCon Sweden, presenting a talk on architecting and building `pycrastinate`, a language-agnostic tool for managing technical debt in large codebases using Git.
            \href{https://www.isaacbernat.com/pycrastinate}{\underline{Companion repository in GitHub}}
        }
    \resumeItemListEnd
\vspace{-1.0em}

    \resumeProjectHeading
        {\textbf{Open Source: netflix-to-srt}}{}
        \resumeItemListStart
            \resumeItem{Creator and maintainer of an open source tool (\textbf{800+ stars on GitHub}) that provides simple solutions for converting multiple subtitle formats, available as a Python CLI and a JavaScript web interface.
            \href{https://www.isaacbernat.com/netflix-to-srt}{\underline{Check project repository}}            
            }
        \resumeItemListEnd
\resumeSubHeadingListEnd

%----------------------------------------------------------------------------------------
%   SKILLS
%----------------------------------------------------------------------------------------
% \vspace{0.5em plus 0.3em minus 0.2em}

\section{Core Competencies}
\begin{itemize}[leftmargin=0.05in, label={}]
    \small{\item{
        \textbf{Programming Languages:}{ \hfill Python (Expert), Go, SQL, JavaScript, C++} \\
        \textbf{Platforms \& Databases:}{ \hfill AWS, PostgreSQL, Docker, Git, MySQL, Redshift, CI/CD (Jenkins, GitHub Actions)} \\
        \textbf{Architecture \& Design:}{ \hfill Distributed Systems, APIs (GraphQL, REST), AI-Assisted Development, Data Pipelines} \\
        \textbf{Practices \& Methodologies:}{ \hfill A/B Testing, TDD, Product Strategy, Incident Management, Cross-Functional Leadership} \\
    }}
\end{itemize}

%----------------------------------------------------------------------------------------
%   EDUCATION & LANGUAGES
%----------------------------------------------------------------------------------------
% \vspace{0.5em plus 0.3em minus 0.2em}


\section{Education \& Languages}
\resumeSubHeadingListStart
    \resumeSubheadingSingleLine % This will now work
        {M.Sc. in Informatics Engineering, \textbf{Highest Honours}}{2006 – 2011}
        {Universitat Politècnica de Catalunya (UPC) \& NTNU}{Barcelona, Spain \& Trondheim, Norway}
        \resumeItemListStart
            \resumeItem{Master's Thesis on Test-Driven Conceptual Modelling conducted at the Norwegian University of Science and Technology (NTNU) as part of the ERASMUS programme.}
            \resumeItem{Awarded the highest possible grade (A with Highest Honours) from both institutions.}
        \resumeItemListEnd

    \vspace{0.5em}
    \resumeSubheadingSingleLine % This will also now work
        {Languages}{}
        {}{}
        \vspace{-1em}
        \resumeItemListStart
            \resumeItem{\textbf{Native:} Catalan, Spanish \textbullet\ \textbf{Full Professional Proficiency:} English (C2) \textbullet\ \textbf{Elementary:} Swedish}
        \resumeItemListEnd
\resumeSubHeadingListEnd


\end{document}
