\documentclass[a4paper]{MagicalCV}
% template based on https://github.com/themagicalmammal/Resume/tree/MagicalCV


\newcommand{\cveventwide}[2]{
  {\small\makebox[0.5\linewidth][l]{\faCalendar \hspace{0.5em}#1}%
  \ifstrequal{#2}{}{}{\makebox[0.5\linewidth][l]{\hspace{0.5em}\hfill#2}}\par}}


% Removing page numbers
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
% Change the geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=.8cm, footskip=.5cm}

% Defining your colors
\definecolor{VividEmerald}{HTML}{046307}
\definecolor{VividPurple}{HTML}{3E0097}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{heading}{VividEmerald}
\colorlet{accent}{VividEmerald}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange, awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-emerald}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

% start document
\begin{document}

% Last update time
\lastupdated

% Title name
\namesection{Isaac}{Bernat}{

\github{GitHub} \href{https://github.com/isaacbernat/cv}{\bf isaacbernat/cv}
\null\hfill
{ Email: \href{mailto:isaac.bernat@gmail.com}{isaac.bernat@gmail.com}}
 \null\hfill
\linkedin{Linkedin} \href{https://www.linkedin.com/in/isaacbernat/}{\bf isaacbernat}
 }

% Column one
\begin{minipage}[t]{0.33\textwidth}

% Achievements
\cvsection{Achievements}
\sectionsep
\subsection{Best 2023 experiment}
\begin{tightemize}
\item {\bf GM}: {\bf +3\% } global Gross Margin.
\item {\bf A/B test:} best out of 215 launched.
\item {\bf Epic lead}: 100\% Backend. Coordinated FE, PM, Data and CRM teams.
\item {\bf Delivery}: 4 weeks ahead of plan.

\end{tightemize}
\sectionsep

\subsection{Subscription model}
\begin{tightemize}
\item {\bf Lead architect}: scaled 2022-03.
\item Represents {\bf 59.3\% GMV} by Q4 2022.
\item {\bf LTV: } {\bf +41\% } YoY in Q2 2022.
\item {\bf ltv/cac: } 1.4x $\rightarrow$ 3.0x in 4 months.
\item {\bf A/B test: } Longest-running so far.
\end{tightemize}
\sectionsep

\subsection{Q\&A page, blog}
\begin{tightemize}
\item {\bf A/B tests: } Q3, Q4 2020.
\item {\bf Blog: } +300\% NPCs.
\item {\bf Q\&A: } +800\% CVR.
\item {\bf Traffic: } 1M new visitors/mo.
\end{tightemize}
\sectionsep

\subsection{1-day improvements}
\begin{tightemize}
\item {\bf Cost control: } Avoid running unnecessary tests (\$31k/yr) - Jun 2022
\item {\bf Hero page: } Phone user on mobile version (+27\% GMV, +20\% hours).

\end{tightemize}
\sectionsep


% Education
\cvsection{Education}

\descript { M.Sc. Thesis in Informatics}
\cvevent{Dec 2011}{\hspace*{-1.3cm} {\bf NTNU} \hspace*{0.2cm} Trondheim, Norway}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
% \begin{tightemize}
% \item \href{https://ntnuopen.ntnu.no/ntnu-xmlui/handle/11250/252845}{\bf TDCM}: Evaluation of Test-Driven Conceptual Modelling.
% \item \href{https://web.archive.org/web/20120806062556/http://www.fib.upc.edu/fib/noticies.html?id=42dccc0a-d955-4bea-9c8e-94b89a95233e}{\bf Grade}: A with Highest Honours.

% \end{tightemize}
\sectionsep
\descript{BE in Informatics}
\cvevent{2006-2011}{\hspace*{-1.0cm}{\bf UPC} \hspace*{0.2cm} Barcelona, Spain}
\sectionsep

% Languages
\cvsection{Languages} \\
\textbf{Native: } Catalan, Spanish. \\
\textbf{Proficient: } English (Cambridge). \\
\textbf{Basic (A2): } Swedish, Norwegian.\\
\sectionsep

% Skills
\cvsection{Backend skills}
\subsection{Python}
\begin{tightemize}
\item {\bf Pycon SE} speaker (2014, 2019). % (https://youtu.be/asZ0SDTKqvM)
\item +30 {\bf microservices}.
\item 3 {\bf Monoliths} (incl. Django).
\item {\bf Scrapping}: +50 sites (scrapy).
\item pytest \textbullet{} PEP8 \textbullet{} ipdb \textbullet{} black...
\end{tightemize}
\sectionsep

\subsection{Other}
\begin{tightemize}
\item {\bf GO}: 12 microservices.
\item {\bf Techs}: PostgreSQL \textbullet{} Unix-like \textbullet{} REST \textbullet{} Git \textbullet{} MySQL \textbullet{} Docker \textbullet{}
 GraphQL \textbullet{} AWS \textbullet{} test \textbullet{} async \textbullet{} ETL \textbullet{} DWH \textbullet{} debug \textbullet{} ...
\item {\bf Optimise}: $10^{18}$x speedup.
\end{tightemize}

% Column two
\end{minipage}
\hfill
\begin{minipage}[t]{0.66\textwidth}

% Experience
\cvsection{Experience}
\sectionsep
\vspace{-1pt}

\runsubsection{Preply.com}
\textcolor{gray}{\fontsize{10pt}{12pt}\selectfont Mar 2020 - current}
\hfill
\descript{Barcelona, Spain}
\cveventwide{Jun 2022 – current}{Senior Backend Engineer I (P7)}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}

\item {\bf Incidents:} command, scribe, mitigate and help fix 15+ up to SEV2. Presented postmortems, including those caused by other teams.
\item {\bf Subscription events:} enabled data teams to track state transitions.
\item {\bf Yearly subscriptions:} implemented multiple periods and policies.
\item {\bf Group lessons:} lead backend and handover project to new team.
\end{tightemize}

\cveventwide{Mar 2020 – Jun 2022}{Backend Engineer III (P6)}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item {\bf Subscriptions:} transition a package-only company:
\begin{tightemize}
\item {\it Backend:} lead architect, re-used existing components for MVP.
\item {\it Volume:} process 150k+ subscription renewals/mo (Q1 2023).
\item {\it Cohorts:} created custom system to support 5 A/B tests in parallel.
\item {\it Features:} cancel, pause, upgrade, downgrade, expire, carry...
\end{tightemize}
\item {\bf Migrate:} {\it Q\&A app} backend from Django templates to GraphQL.
\item {\bf Monitor:} on-call rotation, set up alerts, dashboards (e.g. Grafana).
\item {\bf Interview:} 13 backend candidates. 2 valuable members hired.
\end{tightemize}
\sectionsep
\sectionsep
\sectionsep

\runsubsection{Ivbar.com}
\textcolor{gray}{\fontsize{10pt}{12pt}\selectfont Mar 2018 - Mar 2020}
\hfill
\descript{Stockholm, Sweden}
\cveventwide{Jan 2019 – Mar 2020}{Fullstack Engineer}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item {\bf Chronics:} enabled processing of non-episodic patient groups.
\item {\bf Subgroups:} built case-mix decision trees (multidisciplinary project).
\end{tightemize}

\cveventwide{Mar 2018 – Jan 2019}{Backend Engineer}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item {\bf Processor:} National Quality Registry for Breast Cancer (NKBC).
\item {\bf MECE filters:} made to preserve privacy and avoid triangulation.
\end{tightemize}
\sectionsep
\sectionsep
\sectionsep

\runsubsection{Productos Aditivos}
\textcolor{gray}{\fontsize{10pt}{12pt}\selectfont Jun 2016 - Jan 2018}
\hfill
\textcolor{black}{\fontsize{10pt}{12pt}\selectfont }
\hfill
\descript{Montcada, Spain}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item {\bf As CTO:} market intelligence, ERP migration, transition to SII...
\item {\bf As CFO:} saved 64k EUR on 3y and 7y fix-rate loans.
\end{tightemize}
\sectionsep
\sectionsep
\sectionsep

\runsubsection{Wrapp.com}
\textcolor{gray}{\fontsize{10pt}{12pt}\selectfont Oct 2012 - Jun 2016}
\hfill
\descript{Stockholm, Sweden}
\cveventwide{Sep 2014 – Jun 2016}{Fullstack Engineer}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item {\bf Opsweb:} built web-based AWS deploy system - Dart, Sass and Jade.
\item {\bf Wrappmin:} merchant tool (map transactions, create offers) in React.
\end{tightemize}

\cveventwide{Dec 2013 – Sep 2014}{Data Engineer}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item {\bf Data Warehouse:} designed and optimised ETL pipeline for Redshift.
\item {\bf Wrapport:} delivered reports and features with in-house CRM.
\item {\bf Dashboards:} updated real-time, with business and system KPIs.
\end{tightemize}

\cveventwide{Mar 2013 – Dec 2013}{Web Engineer}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item {\bf Email service:} built framework for pre-flighted design supporting:
\begin{tightemize}
\item {\it A/B test:} subjects, preheader-text, images, conditional render...
\item {\it Compatibility:} +1M weekly newsletters to diverse clients/devices.
\end{tightemize}
\item {\bf Web client:} landing pages, Wrapp 1.0 web app...
\end{tightemize}

\cveventwide{Oct 2012 – Mar 2013}{Backend Engineer}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item {\bf News service:} in-memory (testing), MySQL (production) backends.
\item {\bf Recommender System:} architected and implemented from scratch.
\end{tightemize}
\sectionsep
\sectionsep
\sectionsep

\runsubsection{FXstreet.com}
\textcolor{gray}{\fontsize{10pt}{12pt}\selectfont Feb - Jul 2012}
\hfill
\textcolor{black}{\fontsize{10pt}{12pt}\selectfont Software Developer}
\hfill
\descript{Barcelona, Spain}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item {\bf Maintenance:} 17-language site - C\#, .net MVC3, jQuery on Azure.
\end{tightemize}

\end{minipage}
\end{document}
